\chapter{Conclusion and Recommendations}
\label{chap:conclusion}

\section{Summary of Achievements}

This project successfully designed and implemented a database-driven system for detecting panic selling behavior among individual investors. The key achievements are:

\begin{itemize}
    \item Designed a normalized relational schema with six core tables supporting behavioral analytics workflows.
    \item Generated a realistic synthetic dataset of over [fill in] transaction records across 1,000 investors and nine Vietnamese stock tickers.
    \item Implemented a complete set of advanced database objects: five indexes, three views, two stored procedures, three user-defined functions, and one trigger.
    \item Developed a behavioral analytics pipeline computing DrawdownLevel, SellSpike, and LossSensitivity features, aggregated into a normalized Panic Score.
    \item Built an automated warning system where high Panic Scores trigger advisory warnings without manual intervention.
    \item Delivered a Flask web application providing interactive access to investor profiles, panic scores, and warning dashboards.
\end{itemize}

\section{Limitations}

\begin{itemize}
    \item The synthetic dataset, while behaviorally grounded, does not capture the full complexity of real investor decision-making under varying macroeconomic conditions.
    \item The Panic Score formula uses fixed weights; a machine learning approach could learn optimal weights from labeled real-world data.
    \item The web application is a local prototype and lacks authentication, input validation, and production-grade error handling.
\end{itemize}

\section{Recommendations for Future Work}

\begin{itemize}
    \item \textbf{Richer scenario simulation:} Incorporate macroeconomic events (interest rate changes, geopolitical shocks) into the market regime classification.
    \item \textbf{Explainable AI modules:} Replace the rule-based scoring with an interpretable ML model (e.g., logistic regression or gradient boosting with SHAP explanations) to improve score accuracy.
    \item \textbf{Real data integration:} Connect to live brokerage APIs to compute Panic Scores on real transaction histories.
    \item \textbf{Advisory logic integration:} Feed warning signals into an automated advisory system that generates personalized investment guidance.
    \item \textbf{Real-time pipeline:} Migrate batch processing to a streaming architecture (e.g., Apache Kafka + MySQL binlog) for real-time behavioral monitoring.
\end{itemize}
